### 2025-03-01 README.Rmd
fixed duplicate row ident issue

```{r}
nbsf <- st_bridges(df = uk_election |> filter(country == "Scotland"),
                   row_identifier = "constituency_name",
                   link_islands_k = 2)
```

>>>>

```{r}
scotland_df <- uk_election |> filter(country == "Scotland")
nbsf <- st_bridges(df = scotland_df,
                   row_identifier = "constituency_name",
                   link_islands_k = 2)
```
